---
title: "[LearnLab10] Preprocessing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Reading the Transactions Data

We read the transactions from the two data files, remove one extra column from `SV` (column 35) and concatenate:
```{r read, cache=TRUE}
HW <- read.csv('data/Hopewell2015.csv', header=TRUE, as.is=TRUE)
SV <- read.csv('data/SV2015.csv', header=TRUE, as.is=TRUE)

# Remove extra column
SV <- SV[,-35]

# Stack data frames into one
df <- rbind(HW, SV)
```

We now have a dataframe with `r dim(df)[1]` rows (transactions) and `r dim(df)[2]` columns (variables). We remove all the transactions corresponding to demographic questions:
```{r demographic}
df <- df[-grep('demographic', df$ProblemName, ignore.case = TRUE),]
```

We also remove duplicate transactions (if any) and students from the blacklist:
```{r blacklist}
blacklist <- read.csv('data/StudentBlacklist', sep=";", as.is=TRUE,
                      header=FALSE)[,1]

df <- df %>% distinct() %>%
  filter(!toupper(Anon.Student.Id) %in% blacklist)
```

Finally, we remove extra Test students that were not in the blacklist:
```{r moretest}
# Can probably be done using 'filter' in dplyr
itest <- grep('^Test', df$Anon.Student.Id, perl=TRUE, invert=TRUE)
df <- df[itest,]

Student.list <- unique(df$Anon.Student.Id)
```

The dataframe now has `r dim(df)[1]` transactions and `r dim(df)[2]` variables.

## Compute the enjoyment score, per student

[tbc]

## Computing the correct rate per student

We define a function that computes the correctness rate per student and apply it to all students, through the `Outcome` variable (using the `dplyr` package):
```{r correctrate}
correct.rate <- function(v) {
  inco <- length(grep('incorrect', v, ignore.case=TRUE))
  all <- length(grep('correct', v, ignore.case=TRUE))
  (all-inco)/all
}

student.outcome <- df %>% group_by(Anon.Student.Id) %>% summarise( correct.rate(Outcome))
```

## Retrieving the condition for each student

The condition is "game" (=1) or "non game" (=0). We proceed as before using a function that inspects the `Condition.Name` variable:
```{r condition}
nongame <- function(v) {
  ifelse( length(grep('^NonGame', v, perl=TRUE))>1, 0, 1)
}

student.condition <- df %>% group_by(Anon.Student.Id) %>% summarise( nongame(Condition.Name))
```

## Save results

We build a dataframe with correct rate and condition, per student, and save it:
```{r save}
student.df <- data.frame(Student=student.outcome$Anon.Student.Id,
                         Outcome=student.outcome$`correct.rate(Outcome)`,
                         Condition=student.condition$`nongame(Condition.Name)`) 
write.csv(student.df, "../StudentOutcome.csv")
```